---
title: "| EEEB UN3005/GR5005\n| Lab - Week 04 - 18 and 20 February 2019"
author: "USE YOUR NAME HERE"
output: pdf_document
fontsize: 12pt
---

```{r setup, include = FALSE}

knitr::opts_chunk$set(echo = TRUE)
```


# Bayesian Basics


## Exercise 1: Applying Bayes' Theorem using Grid Approximation

Imagine the series of observations in the globe tossing example from the *Statistical Rethinking* text and class were: W L W W, where "W" corresponds to water and "L" corresponds to land.

With this set of observations, use grid approximation (with 11 grid points) to construct the posterior for *p* (the probability of water). Assume a flat prior.

Plot the posterior distribution.

```{r}

```


## Exercise 2: Thinking Deeper with Bayes' Theorem

Suppose in the globe tossing scenario there are two globes, one for Earth and one for Mars. The Earth globe is 70% covered in water. The Mars globe is 100% land. Further suppose that one of these globes—you don’t know which—was tossed in the air and produced a “land” observation. Assume that each globe was equally likely to be tossed. Show that the posterior probability that the globe was the Earth, conditional on seeing “land” (Pr(Earth|land)), is 0.23.

Note, this problem might seem like it has a lot of information to consider, but it is actually a direct application of Bayes' Theorem. If you're having problems getting started, write out Bayes' Theorem. Also, R is not strictly necessary for this problem. You could do the math by hand, so R is just a glorified calculator here.

```{r}

```
